Compilation With Program Synthesis

### 2023-08-22 new-paper/examples.tex
bibliography; a few sentences on layout polymorphism
Pika 2 examples
Some stats for Pika 2 examples
Description of the example tables

@@

>>>>

Working \Pika{} 1 examples are presented in Figure~\ref{size-comparison}. For each example, we compare the AST size of the \Pika{} code with that of the generated \SuSLik{} code. This is a rough measure of the relative expressiveness of \Pika{} and \SuSLik{} on these examples. Each example in the list consists of a single function which was tested by hand.

\begin{figure}[b]
\setlength{\abovecaptionskip}{5pt}
\setlength{\belowcaptionskip}{-15pt}
\begin{center}
  \begin{table}[H]
  \begin{tabular}{ c c c c }
    \hline
    Name & \suslik size & \tool 1 size & \tool 1 size / \suslik size\\
    \hline
    \verb|append| & 164 & 84 & 0.512 \\
    \verb|cons| & 82 & 52 & 0.634 \\
    \verb|filterLt9| & 136 & 66 & 0.485 \\
    \verb|singleton| & 70 & 47 & 0.671 \\
    \verb|map| & 147 & 93 & 0.633 \\
    \verb|mapSum| & 138 & 97 & 0.703 \\
    \verb|maximum| & 106 & 61 & 0.575 \\
    \verb|leftList| & 144 & 104 & 0.722 \\
    \verb|take| & 180 & 112 & 0.622
  \end{tabular}
  \end{table}
\end{center}
  \caption{\tool 1 spec size vs generated SSL spec size measured in number of AST nodes}
  \label{fig:size-comparison}
\end{figure}

@@

Figure~\ref{fig:pika-2-examples} is a table of \Pika{} 2 examples together with the number of functions they have (not including \synth) and whether or not they use \synth. These functions were tested using the unit testing framework built into \Pika{} 2.

\begin{figure}
  \begin{tabular}{ c c c }
    \hline
    Name & \# of functions & Uses \synth\\
    \hline
    \verb|add1Head| & 1 & No\\
    \verb|anagram| & 4 & No\\
    \verb|fact| & 1 & No\\
    \verb|filterLt| & 1 & No\\
    \verb|heap| & 6 & Yes\\
    \verb|leftList| & 1 & No\\
    \verb|mapAdd| & 1 & No\\
    \verb|maximum| & 1 & No\\
    \verb|set| & 3 & Yes\\
    \verb|sum| & 1 & No\\
    \verb|take| & 1 & No\\
    \verb|treeSize| & 1 & No\\
  \end{tabular}
  \caption{\Pika{} 2 examples}
  \label{fig:pika-2-examples}
\end{figure}
